Functions relating to the Colonization model

### 2018-03-21 AlgebraProblem/CorrAndCovFunction.Rmd
Saved

dataGROut <-filter(fdata,species== "GR" & location== "O")[,c(1,6,7,8)]
colnames(dataGROu)<-c("ind","c1","c2","pop")
Bcor(dataGROu)
Icor(dataGROu)

@@

dataSC <-filter(fdata,species== "SC")[,c(1,6,7,8)]
colnames(dataSC)<-c("ind","c1","c2","pop")
Bcor(dataSC)
Icor(dataSC)
```

>>>>

dataGROut <-filter(fdata,species== "GR" & location== "O")[,c(1,6,7,8)]
colnames(dataGROut)<-c("ind","c1","c2","pop")
Bcor(dataGROut)
Icor(dataGROut)

@@

dataSCIn <-filter(fdata,species== "SC" & location== "I")[,c(1,6,7,8)]
colnames(dataSCIn)<-c("ind","c1","c2","pop")
Bcor(dataSCIn)
Icor(dataSCIn)

dataSCOut <-filter(fdata,species== "SC" & location== "O")[,c(1,6,7,8)]
colnames(dataSCOut)<-c("ind","c1","c2","pop")
Bcor(dataSCOut)
Icor(dataSCOut)
